### 2023-01-24 Poisot_et_al_2023_template_prepare_draft.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@ff6a660bd329ca2c1099a5e8976df8c23074179b 🚀
Deploying to gh-pages from @ PoisotLab/manuscript-template@2fa588414a595ad382e315343a735c4f6e80d7c7 🚀

@@

\textbf{Correspondance to:}\\

@@

\begin{verbatim}
[auth:fold]
[year]
[title:fold:nopunctordash:skipwords:lower:select=1,1:substring=1,3:capitalize]
[title:fold:nopunctordash:skipwords:lower:select=2,2:substring=1,3:capitalize]
\end{verbatim}

>>>>

\usepackage{gensymb}

@@

\textsuperscript{‡}\,Equal contributions\\

\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\

@@

\begin{verbatim}
auth.fold.fold + year + title.fold.nopunctordash.skipwords.lower.select(1,1).capitalize()
\end{verbatim}
